---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# csgc

<!-- badges: start -->
<!-- badges: end -->

The goal of csgc is to perform statistical analysis of network data based on centred subgraph counts.

## Installation

You can install the development version of csgc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lishang-stats/csgc")
```

## Example

Assume an undirected unweighted network has $n$ vertices, with $A$ be the adjacency matrix and $P$ be the corresponding probability matrix. The parameter matrix $K$ (a $k$ by $k$ matrix) presents the connection probability within/between each block. Let $z$ be the label vector with length $n$, where each entry can be from $1$ to $k$. Consider the Bernoulli-type Stochastic Block Model
![equation](https://latex.codecogs.com/png.image?\dpi{200}A_{ij}=A_{ji}\overset{i.i.d.}{\sim} \mathop{\mathrm{Be}}(k_{z_iz_j}), \quad\text{for $1\leq i,j\leq n, i\ne j$})
. We first generate matrix $A$ and $P$ from $K$.

```{r example}
set.seed(123)
library(csgc)
k = 4
n = 200
K = matrix(0,k,k)
K[upper.tri(K,diag=T)] = runif(k*(k+1)/2)
K[lower.tri(K,diag=T)] = t(K)[lower.tri(K,diag=T)]
z = rep(1:k,each=n/k)
# mat = gen_adj_sbm(K,z)
# A = mat$A
# P = mat$P
## basic example code
```

