---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# csgc

<!-- badges: start -->
<!-- badges: end -->

The goal of csgc is to perform statistical analysis of network data based on centred subgraph counts.

## Installation

You can install the development version of csgc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lishang-stats/csgc")
```

## Example

Assume an undirected network has $n$ vertices, with $A=(A_{ij})_{nn}$ be the adjacency matrix and `$A_{ii}= 0$` for all $i$. Suppose the parameter matrix is $K=(k_{rs})_{k\times k}$. Let $z=(z_1,\dots,z_n)$ be the label vector, where $z_i=r$ means the $i$-th vertex is in group $r$. Consider the Bernoulli-type Stochastic Block Model, i.e.
$$A_{ij}=A_{ji}\overset{i.i.d.}{\sim} \text{Be}(k_{z_iz_j})$$
for $1\leq i,j\leq n, i\ne j$. We first generate matrix $A$ and $P$ from $K$.

```{r example}
library(csgc)
## basic example code
```

